problem years

### 2024-08-12 src/problem_years.Rmd
LAD lisa

```{r}
n = 1 #number of unique postcodes. 
m = 11

@@

df.long %>% 
  mutate(year = as.double(year)) %>% 
  ggplot() +
  geom_line(mapping = aes(x = year, y = n, group = pc), alpha = .3, size = .2) +
  ylab("N. of websites per postcode") +
  scale_x_continuous(breaks=seq(1996, 2012, 1)) +
  scale_y_continuous(labels=scales::comma) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5)) +
  geom_text_repel(aes(x = year, y = n, label=outlier), cex = 3)

path.out <- paste0(path, "/outputs/pc_year_1.png")
ggsave(path.out, bg='#ffffff')  
```

@@

df.corrected %>% 
  as_tibble() %>% 
  mutate(year = as.double(as.character(year))) %>% 
  ggplot() +
  geom_line(mapping = aes(x = year, y = n, group = pc), alpha = .3, size = .2) +
  ylab("N. of websites per postcode") +
  scale_x_continuous(breaks=seq(1996, 2012, 1)) +
  scale_y_continuous(labels=scales::comma) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5))

path.out <- paste0(path, "/outputs/pc_year_1_corrected.png")
ggsave(path.out, bg='#ffffff')  
```

@@

@@

theme(axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks = element_blank(),
        rect = element_blank())

>>>>

```{r}
n = 1 #number of unique postcodes. 
#m = 11

@@

path.out <- paste0(path, "/outputs/pc_year_1.png")

df.long %>% 
  mutate(year = as.double(year)) %>% 
  ggplot() +
  geom_line(mapping = aes(x = year, y = n, group = pc), alpha = .3, size = .2) +
  ylab("N. of websites per postcode") +
  scale_x_continuous(NULL, breaks=seq(1996, 2012, 1)) +
  scale_y_continuous(labels=scales::comma) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5),
          panel.grid.minor.x = element_blank()) 
  #geom_text_repel(aes(x = year, y = n, label=outlier), cex = 3)

ggsave(path.out, bg='#ffffff')  
```

@@

path.out <- paste0(path, "/outputs/pc_year_1_corrected.png")

df.corrected %>% 
  as_tibble() %>% 
  mutate(year = as.double(as.character(year))) %>% 
  ggplot() +
  geom_line(mapping = aes(x = year, y = n, group = pc), alpha = .3, size = .2) +
  ylab("N. of websites per postcode") +
  scale_x_continuous(NULL, breaks=seq(1996, 2012, 1)) +
  scale_y_continuous(labels=scales::comma) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5),
          panel.grid.minor.x = element_blank())

ggsave(path.out, bg='#ffffff')  
```

@@

#spatial weight matrix moved out of the loop

@@

theme(axis.text.x = element_blank(),
      axis.text.y = element_blank(),
      axis.ticks = element_blank(),
      rect = element_blank(),
      plot.margin = unit(c(0, 0, 0, 0), "cm"))
